---
title: "ECON4"
author: "Marcos Jaramillo Restrepo"
date: "2024-06-26"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
# Load Packages
library(shiny)
library(ggplot2)

# Prepare Data
data2 <- data.frame(
  Estudiante = as.factor(1:30),
  Rendimiento = c(3.3, 3.3, 3.3, 4.2, 3.8, 4.2, 3.8, 3.8, 4.6, 3.3, 4.2, 5, 5, 4.6, 3.3, 1.7, 2.9, 4.2, 2.5, 2.9, 2.5, 2.9, 3.8, 4.2, 2.9, 4.2, 2.5, 2.5, 3.8, 3.8),
  GeneroF = as.numeric(c(1,1,0,1,1,1,1,0,0,0,1,1,0,0,1,0,0,1,0,0,0,1,0,0,1,1,1,0,1,0)),
  Exdig = as.numeric(c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)),
  Edad = as.numeric(c(21, 19, 20, 22, 23, 21, 20, 22, 20, 21, 20, 21, 17, 21, 19, 23, 18, 19, 23, 19, 21, 18, 22, 20, 23, 21, 19, 17, 18, 23)),
  Estrato = as.numeric(c(5,4,4,4,5,5,5,6,3,6,6,6,6,4,5,4,6,6,6,4,4,4,4,5,3,6,3,4,4,5))
)

# Linear Model
modelo <- lm(Rendimiento ~ Exdig + GeneroF + Edad + Estrato, data = data2)

# Shiny UI
ui <- fluidPage(
  titlePanel("Regresion Linear Multiple"),
  sidebarLayout(
    sidebarPanel(
      numericInput("genero_input", "Genero (F = 1, M = 0):", value = 1, min = 0, max = 1),
      numericInput("exdig_input", "Tipo de examen (Exdig = 1, Otros = 0):", value = 1, min = 0, max = 1),
      numericInput("edad_input", "Edad:", value = 23, min = 17, max = 23),
      numericInput("estrato_input", "Estrato socioeconomico:", value = 6, min = 3, max = 6),
      actionButton("predict_button", "Predecir"),
      hr(),
      h4("Model Coefficients:"),
      verbatimTextOutput("coefficients_text")
    ),
    mainPanel(
      style = "background-color: #C0B8B8;",  # Background color change
      plotOutput("regression_plot"),
      h4("Rendimiento predecido (Y) :"),
      verbatimTextOutput("Rendimiento_predecido")
    )
  )
)
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
# Shiny server
server <- function(input, output) {
  # Predict function
  predict_knowledge <- function(GeneroF, Exdig, Edad, Estrato) {
    new_data <- data.frame(GeneroF = GeneroF, Exdig = Exdig, Edad = Edad, Estrato = Estrato)
    predicted_knowledge <- predict(modelo, newdata = new_data)
    return(predicted_knowledge)
  }
  
  # Render combined plot for all variables
  output$regression_plot <- renderPlot({
    ggplot(data2, aes(x = GeneroF, y = Rendimiento)) +
      geom_point(aes(color = "GeneroF"), size = 3) +
      geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
      geom_point(aes(x = Exdig , color = "Exdig"), size = 3) +
      geom_point(aes(x = Edad, color = "Edad"), size = 3) +
      geom_point(aes(x = Estrato , color = "Estrato"), size = 3) +
      labs(title = "Multiple Linear Regression",
           x = "GeneroF, Exdig, Edad y Estrato",
           y = "Rendimiento (Y)",
           color = "Variable") +
      theme_minimal()
  })
  
  # Render coefficients
  output$coefficients_text <- renderText({
    paste("Intercepto:", round(coef(modelo)[1], 4),
          "Genero:", round(coef(modelo)[2], 4),
          "Tipo de examen:", round(coef(modelo)[3], 4),
          "Edad:", round(coef(modelo)[4], 4),
          "Estrato:", round(coef(modelo)[5], 4))
  })
  
  # Event handler for prediction button
  observeEvent(input$predict_button, {
    genero_input <- input$genero_input
    exdig_input <- input$exdig_input
    edad_input <- input$edad_input
    estrato_input <- input$estrato_input
    rendimiento_predecido <- predict_knowledge(genero_input, exdig_input, edad_input, estrato_input)
    output$Rendimiento_predecido <- renderText({
      paste("Rendimiento predecido (Y):", round(rendimiento_predecido, 2))
    })
  })
}
# Run Shiny app
shinyApp(ui, server)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



